\begin{abstract}
In the dynamic and high-stakes world of sports betting, effective predictive modeling and bankroll management are crucial for maximizing returns while mitigating risks. This report presents the development and implementation of a comprehensive system designed to optimize sports betting strategies, with a focus on football matches. The system is grounded in a theoretical framework that models the interactions between two agents—the bettor and the bookmaker—where, at each time \( t \), the bettor allocates a fraction of their bankroll across possible outcomes, and the bookmaker sets the odds for each outcome. To manage the complexities inherent in dynamic betting environments, we simplify the problem by transitioning from a dynamic optimization framework to a static one, allowing for tractable solutions and efficient computations.

Leveraging predictive models, including logistic regression, and utility-based optimization techniques such as the Kelly Criterion, the system aims to forecast match outcomes probabilites accurately and allocate betting capital efficiently. The architecture integrates data collection from various sources, predictive modeling, optimization algorithms, and deployment on a cloud-based infrastructure using Kubernetes on Azure. Through both Monte Carlo simulations and real-world online testing over a five-week period, the strategies were evaluated for performance and robustness. 

The results demonstrate that sophisticated utility-based strategies significantly outperform naive betting approaches, achieving higher returns and better risk management. The transition to a static framework enables the effective application of these strategies in a practical setting. The deployment of the system on Azure Kubernetes Service (AKS) ensures scalability, reliability, and the ability to handle real-time data processing demands. Limitations and future enhancements are discussed, including the incorporation of more complex models and dynamic risk preferences. This work contributes to the field of sports analytics by providing a practical framework for optimized betting strategies in a real-world environment, grounded in a solid theoretical foundation.
\end{abstract}