\chapter{All Feature Descriptions}
\label{appendix:all_feature_descriptions}

\section{Team Ratings and Statistics}
\begin{itemize}
    \item \textbf{home\_attack}: Attack rating of the home team.
    \item \textbf{away\_attack}: Attack rating of the away team.
    \item \textbf{home\_club\_worth}: Total club worth of the home team.
    \item \textbf{away\_club\_worth}: Total club worth of the away team.
    \item \textbf{home\_defence}: Defence rating of the home team.
    \item \textbf{away\_defence}: Defence rating of the away team.
    \item \textbf{home\_defence\_domestic\_prestige}: Domestic prestige rating for the home team's defence.
    \item \textbf{away\_defence\_domestic\_prestige}: Domestic prestige rating for the away team's defence.
    \item \textbf{home\_midfield}: Midfield rating of the home team.
    \item \textbf{away\_midfield}: Midfield rating of the away team.
    \item \textbf{home\_overall}: Overall rating of the home team.
    \item \textbf{away\_overall}: Overall rating of the away team.
    \item \textbf{home\_players}: Number of players in the home team.
    \item \textbf{away\_players}: Number of players in the away team.
    \item \textbf{home\_starting\_xi\_average\_age}: Average age of the starting eleven for the home team.
    \item \textbf{away\_starting\_xi\_average\_age}: Average age of the starting eleven for the away team.
    \item \textbf{home\_team\_goals\_season\_to\_date\_before\_match}: Total goals scored by the home team up to this point in the season.
    \item \textbf{away\_team\_goals\_season\_to\_date\_before\_match}: Total goals scored by the away team up to this point in the season.
    \item \textbf{home\_team\_number\_of\_match\_played}: Number of matches played by the home team in the season.
    \item \textbf{away\_team\_number\_of\_match\_played}: Number of matches played by the away team in the season.
    \item \textbf{home\_transfer\_budget}: Transfer budget of the home team.
    \item \textbf{away\_transfer\_budget}: Transfer budget of the away team.
    \item \textbf{home\_whole\_team\_average\_age}: Average age of the entire home team.
    \item \textbf{away\_whole\_team\_average\_age}: Average age of the entire away team.
\end{itemize}

\section{League Information}
\begin{itemize}
    \item \textbf{home\_league\_ESP-La Liga}: Indicator if the home team plays in La Liga.
    \item \textbf{away\_league\_ESP-La Liga}: Indicator if the away team plays in La Liga.
    \item \textbf{home\_league\_ENG-Premier League}: Indicator if the home team plays in the Premier League.
    \item \textbf{away\_league\_ENG-Premier League}: Indicator if the away team plays in the Premier League.
    \item \textbf{home\_league\_ITA-Serie A}: Indicator if the home team plays in Serie A.
    \item \textbf{away\_league\_ITA-Serie A}: Indicator if the away team plays in Serie A.
    \item \textbf{home\_league\_GER-Bundesliga}: Indicator if the home team plays in the Bundesliga.
    \item \textbf{away\_league\_GER-Bundesliga}: Indicator if the away team plays in the Bundesliga.
    \item \textbf{home\_league\_FRA-Ligue 1}: Indicator if the home team plays in Ligue 1.
    \item \textbf{away\_league\_FRA-Ligue 1}: Indicator if the away team plays in Ligue 1.
    \item \textbf{home\_league\_INT}: Indicator if the home team plays in an international league.
    \item \textbf{away\_league\_INT}: Indicator if the away team plays in an international league.
\end{itemize}


\section{Prestige Ratings}
\begin{itemize}
    \item \textbf{home\_international\_prestige}: International prestige rating for the home team.
    \item \textbf{away\_international\_prestige}: International prestige rating for the away team.
\end{itemize}

\section{Elo, Glicko-2 and Trueskill Ratings}
\begin{itemize}
    \item \textbf{elo\_home\_before}: Elo rating of the home team before the match.
    \item \textbf{elo\_away\_before}: Elo rating of the away team before the match.
    \item \textbf{glicko2\_home\_before}: Glicko-2 rating for the home team before the match.
    \item \textbf{glicko2\_away\_before}: Glicko-2 rating for the away team before the match.
    \item \textbf{glicko2\_rd\_home\_before}: Glicko-2 rating deviation for the home team before the match.
    \item \textbf{glicko2\_rd\_away\_before}: Glicko-2 rating deviation for the away team before the match.
    \item \textbf{glicko2\_vol\_home\_before}: Glicko-2 volatility for the home team before the match.
    \item \textbf{glicko2\_vol\_away\_before}: Glicko-2 volatility for the away team before the match.
    \item \textbf{trueskill\_home\_before}: TrueSkill rating for the home team before the match.
    \item \textbf{trueskill\_away\_before}: TrueSkill rating for the away team before the match.
\end{itemize}

\section{Build-up and Passing Styles}
\begin{itemize}
    \item \textbf{home\_build\_up\_passing\_Mixed}: Mixed passing buildup style for the home team.
    \item \textbf{away\_build\_up\_passing\_Mixed}: Mixed passing buildup style for the away team.
    \item \textbf{home\_build\_up\_passing\_Short}: Short passing buildup style for the home team.
    \item \textbf{away\_build\_up\_passing\_Short}: Short passing buildup style for the away team.
    \item \textbf{home\_build\_up\_positioning\_Organised}: Organized buildup play for the home team.
    \item \textbf{away\_build\_up\_positioning\_Organised}: Organized buildup play for the away team.
    \item \textbf{home\_build\_up\_speed\_Fast}: Fast buildup play for the home team.
    \item \textbf{away\_build\_up\_speed\_Fast}: Fast buildup play for the away team.
    \item \textbf{home\_build\_up\_speed\_Slow}: Slow buildup play for the home team.
    \item \textbf{away\_build\_up\_speed\_Slow}: Slow buildup play for the away team.
\end{itemize}

\section{Chance Creation and Shooting Styles}
\begin{itemize}
    \item \textbf{home\_chance\_creation\_crossing\_Lots}: High volume crossing chance creation for the home team.
    \item \textbf{away\_chance\_creation\_crossing\_Lots}: High volume crossing chance creation for the away team.
    \item \textbf{home\_chance\_creation\_crossing\_Normal}: Normal crossing chance creation for the home team.
    \item \textbf{away\_chance\_creation\_crossing\_Normal}: Normal crossing chance creation for the away team.
    \item \textbf{home\_chance\_creation\_passing\_Risky}: Risky passing for chance creation by the home team.
    \item \textbf{away\_chance\_creation\_passing\_Risky}: Risky passing for chance creation by the away team.
    \item \textbf{home\_chance\_creation\_passing\_Safe}: Safe passing for chance creation by the home team.
    \item \textbf{away\_chance\_creation\_passing\_Safe}: Safe passing for chance creation by the away team.
    \item \textbf{home\_chance\_creation\_positioning\_Organised}: Organized chance creation for the home team.
    \item \textbf{away\_chance\_creation\_positioning\_Organised}: Organized chance creation for the away team.
    \item \textbf{home\_chance\_creation\_shooting\_Lots}: High volume shooting chance creation for the home team.
    \item \textbf{away\_chance\_creation\_shooting\_Lots}: High volume shooting chance creation for the away team.
    \item \textbf{home\_chance\_creation\_shooting\_Normal}: Normal shooting chance creation for the home team.
    \item \textbf{away\_chance\_creation\_shooting\_Normal}: Normal shooting chance creation for the away team.
\end{itemize}

\section{Defensive Strategies}
\begin{itemize}
    \item \textbf{home\_defence\_aggression\_Double}: Double marking defensive aggression for the home team.
    \item \textbf{away\_defence\_aggression\_Double}: Double marking defensive aggression for the away team.
    \item \textbf{home\_defence\_aggression\_Press}: Pressing defensive aggression for the home team.
    \item \textbf{away\_defence\_aggression\_Press}: Pressing defensive aggression for the away team.
    \item \textbf{home\_defence\_defender\_line\_Offside\_trap}: Use of offside trap in the home team's defensive line.
    \item \textbf{away\_defence\_defender\_line\_Offside\_trap}: Use of offside trap in the away team's defensive line.
    \item \textbf{home\_defence\_pressure\_High}: High pressure defensive strategy for the home team.
    \item \textbf{away\_defence\_pressure\_High}: High pressure defensive strategy for the away team.
    \item \textbf{home\_defence\_pressure\_Medium}: Medium pressure defensive strategy for the home team.
    \item \textbf{away\_defence\_pressure\_Medium}: Medium pressure defensive strategy for the away team.
    \item \textbf{home\_defence\_team\_width\_Normal}: Normal defensive width for the home team.
    \item \textbf{away\_defence\_team\_width\_Normal}: Normal defensive width for the away team.
    \item \textbf{home\_defence\_team\_width\_Wide}: Wide defensive width for the home team.
    \item \textbf{away\_defence\_team\_width\_Wide}: Wide defensive width for the away team.
\end{itemize}

